The Count Distinct Problem

### 2015-11-06 wim/paper.tex
conclusion

We can use the hash table, the Linear Probabilistic Counter, and the HyperLogLog to solve each problem, respectively.
\\\\

@@

The pok\'emon problem provides a good example of the benefits of a hash table.
\\\\

@@

\indent The LPC algorithm is divided into several steps. In the first step, the algorithm creates an arbitrarily sized bitmap in memory, and then hashes the values into the bitmap by determining the address in the bitmap at which the corresponding bit should be changed to a 1.

@@

Figure 2 shows the Ruby implementation of the LPC algorithm.

@@

\noindent The LPC algorithm also allows us to specify the amount of error we are willing to tolerate.

@@

\indent We can use the LPC algorithm to solve the Facebook problem; unfortunately, we have no way of accessing the actual data we need, so we will have to do some guessing. 

@@

We also need a hashing function that will produce a binary string of 1's and 0's given any key; luckily this hash function already exists. A murmur hash will produce a 32 bit binary string, which is exactly what we need.

@@

@@

The count distinct problem

>>>>

We can use the hash table, the Linear Probabilistic Counter, and the HyperLogLog to solve each problem, respectively.\\

@@

The pok\'emon problem provides a good example of the benefits of a hash table.\\

@@

\indent The Linear Probabilistic Counter algorithm is divided into several steps. In the first step, the algorithm creates an arbitrarily sized bitmap in memory, and then hashes the values into the bitmap by determining the address in the bitmap at which the corresponding bit should be changed to a 1.

@@

Figure 2 shows the Ruby implementation of the Linear Probabilistic Counter algorithm.

@@

\noindent The Linear Probabilistic Counter algorithm also allows us to specify the amount of error we are willing to tolerate.

@@

\indent We can use the Linear Probabilistic Counter algorithm to solve the Facebook problem; unfortunately, we have no way of accessing the actual data we need, so we will have to do some guessing. 

@@

We also need a hashing function that will produce a binary string of 1's and 0's given any key; luckily this hash function already exists. 

@@

A murmur hash will produce a 32 bit binary string, which is exactly what we need.

@@

The count distinct problem is heavily applicable in the real world; companies are able to turn the numbers that are determined by algorithms such as the HyperLogLog to increase profits, target ads, and keep more data.
Finding an efficient way to count large sets of data may never be competely accurate, but with algorithms like the HyperLogLog and the Linear Probabilistic counter, we can efficiently and with nearly 100\% accuracy solve the count distinct problem.
